Regional Inequalities and economic growth; cross section and times series analysis

### 2023-10-24 MSB104_GR_1_Final_Assignment_research_article.qmd
litteratur liste

@@

After calculating the GDP per capita for all NUTS 3 regions countries, we can see that there is a large spread between the figures for the various regions. We want to look at regional inequity; in order to do this in a valuable way, countries are divide. Furthermore, gaining important insights on regional differences and utilize. Later to discuss national policy on equity and sustainable economic development in regions.

#

>>>>

### Cross sectional analysis

@@

After calculating the GDP per capita for all NUTS 3 regions within the chosen countries, we can see that there is a large spread between the figures for the various regions. We want to look at regional inequity; in order to do this in a valuable way, countries are divide. Furthermore, gaining important insights on regional differences and utilize. Later to discuss national policy on equity and sustainable economic development in regions.

### Portugal
